---
title: "Financial Econometrics Project - Forecasting 5 Equity Stock Exchanges Globally
  with reports on each."
output:
  html_notebook: default
  pdf_document: default
---

[**Installing and Loading Required Libraries**]{.underline}

```{r}
# # Required Packages
packages = c('quantmod','car','forecast','tseries','FinTS', 'rugarch','utf8','ggplot2')
# 
# # Install all Packages with Dependencies
# install.packages(packages, dependencies = TRUE)
# 
# # Load all Packages
lapply(packages, require, character.only = TRUE)
library(writexl)
library(tseries)
library(TSstudio)
library(fBasics)
library(rcompanion)
library(forecast)
library(lmtest)
library(tsDyn)
library(vars)
library(PerformanceAnalytics)
library(vrtest)
library(pracma)
library(rugarch)
library(FinTS)
library(e1071)
library(readxl)
```

```{r}
# Fetching Data
symbols <- c("^BSESN","^GSPC","^N225","^HSI","^N100")
getSymbols(Symbols = symbols,
           src = 'yahoo',
           from = as.Date('2018-01-01'),
           to = as.Date('2023-12-31'),
           periodicity = 'daily')
```

The names of the stock exchanges selected

	1.	**\^BSESN** - SENSEX (BSE Sensex) of the **Bombay Stock Exchange (BSE)-**

The Bombay Stock Exchange (BSE), located in Mumbai, India, is one of the oldest stock exchanges in Asia, founded in 1875. The BSE Sensex, or SENSEX, is its benchmark index, representing 30 of the largest and most actively traded stocks on the exchange, reflecting the overall performance of the Indian stock market.

	2.	**\^GSPC** - S&P 500 Index of the **New York Stock Exchange (NYSE) and NASDAQ**

The S&P 500 Index tracks the performance of 500 large companies listed on the New York Stock Exchange (NYSE) and NASDAQ. It is widely regarded as one of the best gauges of the U.S. stock market’s health and is a common benchmark for investment performance.

	3.	**\^N225** - Nikkei 225 Index of the **Tokyo Stock Exchange**

The Nikkei 225 is a stock market index for the Tokyo Stock Exchange (TSE), Japan’s premier stock exchange. It comprises 225 of the largest and most liquid stocks in Japan, serving as a key indicator of the Japanese economy and stock market trends.

	4.	**\^HSI** - Hang Seng Index of the **Hong Kong Stock Exchange (HKEX)**

The Hang Seng Index (HSI) is the main stock market index of the Hong Kong Stock Exchange (HKEX). It tracks the performance of the largest and most liquid companies listed in Hong Kong, providing insight into the broader economic health of Hong Kong and China.

	5.	**\^N100** - Euronext 100 Index of the **Euronext Stock Exchange** (covers major European markets)

The Euronext 100 Index represents the largest and most liquid stocks traded on the Euronext Stock Exchange, which operates in several European countries, including France, Belgium, Netherlands, and Portugal. The index includes 100 blue-chip companies, reflecting the performance of major European markets.

**Cleaning the Data**

```{r}
# Cleaning Data
BSESN <- na.omit(BSESN$BSESN.Close)
GSPC <- na.omit(GSPC$GSPC.Close)
N225 <- na.omit(N225$N225.Close)
HSI <- na.omit(HSI$HSI.Close)
N100 <- na.omit(N100$N100.Close)
```

**Taking Log Returns of the Chosen Exchanges and Testing Stationarity**

Checking Stationarity of the Data:

Used Test: **Augmented Dicky Fuller's Test**

**H0**: The series is not stationary

**H1**: The series is stationary

1.  **BSESN**

```{r}
# Log Differencing and ADF Test
LRBSESN <- diff(log(BSESN))
LRBSESN <- na.omit(LRBSESN)
adf.test(LRBSESN)
```

**Results -** p-value \<0.05 Hence We Reject H0

2.  **GSPC**

```{r}
LRGSPC <- diff(log(GSPC))
LRGSPC <- na.omit(LRGSPC)
adf.test(LRGSPC)
```

**Results -** p-value \<0.05 Hence We Reject H0

3.  **N225**

```{r}
LRN225 <- diff(log(N225))
LRN225 <- na.omit(LRN225)
adf.test(LRN225)
```

**Results -** p-value \<0.05 Hence We Reject H0

4.  **HSI**

```{r}
LRHSI <- diff(log(HSI))
LRHSI <- na.omit(LRHSI)
adf.test(LRHSI)
```

**Results -** p-value \<0.05 Hence We Reject H0

5.  **N100**

```{r}
LRN100 <- diff(log(N100))
LRN100 <- na.omit(LRN100)
adf.test(LRN100)
```

**Results -** p-value \<0.05 Hence We Reject H0

**Normality Test** for all Series:

Used Test: **Jarque Bera Test**

**H0**: The series is normally ditsributed

**H1**: The series is not normally distributed

```{r}
jarque.bera.test(LRBSESN)
jarque.bera.test(LRGSPC)
jarque.bera.test(LRN225)
jarque.bera.test(LRHSI)
jarque.bera.test(LRN100)
```

**Explanation:**

p-value for all 5 series is less than 0.05

hence we reject the null hypothesis and say that all the series are not normally distributed

Implication: all the 5 return series are risky stock exchanges

**Plotting all 5 Stock Exchanges**

```{r}
plotNormalHistogram(LRBSESN)
plotNormalDensity(LRBSESN)
plotNormalHistogram(LRGSPC)
plotNormalDensity(LRGSPC)
plotNormalHistogram(LRN225)
plotNormalDensity(LRN225)
plotNormalHistogram(LRHSI)
plotNormalDensity(LRHSI)
plotNormalHistogram(LRN100)
plotNormalDensity(LRN100)
```

**Obtaining Basic Statistics of Log Returns of Each Stock Exchanges**

```{r}
# Print Basic Stats 
basicStats(LRBSESN)
basicStats(LRGSPC)
basicStats(LRN225)
basicStats(LRHSI)
basicStats(LRN100)
```

**ARIMA Modelling of Return Series**

1.**BSESN**

```{r}
acf(LRBSESN) 
pacf(LRBSESN) 

#Using Auto arima 
arma_pq_LRBSESN = auto.arima(LRBSESN); arma_pq_LRBSESN

#Application of ARIMA

model2 = arima(LRBSESN,order = c(0,0,1))
model2

et = residuals(model2)
et

#Checking of significance of ARMA
coeftest(model2)

#point forecast is called out of sample forecast
autoplot(forecast(model2, h=500))
```
**Explanation:**

1.  **Auto ARIMA:** gave order of ARIMA (0,0,1)

    i.e. no autoregressive (AR) terms, no differencing (D) terms, and one moving average (MA) term.

2.  **Log likelihood:** 4468.7 This is a measure of the model's goodness of fit. A higher log likelihood indicates a better fit.

    **AIC:** -8931.39 The Akaike Information Criterion (AIC) is a measure of model complexity and fit. A lower AIC indicates a better model.

    **sigma\^2:** 0.000137 This is the estimated variance of the residuals, representing the model's ability to fit the data. A smaller value suggests a better fit.

    **Implication:** The ARIMA(0,0,1) model provides a parsimonious representation of the LRNSEI time series. The model suggests that the current value of the series is influenced by the previous period's error.

3.  **The significance test** indicate that the MA1 coefficient in the ARIMA(0,0,1) model is not statistically significant. The intercept coefficient is close to being statistically significant, but more evidence is needed to confirm its significance.

**2.GSPC**

```{r}
acf(LRGSPC) 
pacf(LRGSPC) 

#Using Auto arima 
arma_pq_LRGSPC = auto.arima(LRGSPC); arma_pq_LRGSPC

#Application of ARIMA

model2 = arima(LRGSPC,order = c(4,0,4))
model2

et = residuals(model2)
et

#Checking of significance of ARMA
coeftest(model2)

#point forecast is called out of sample forecast
autoplot(forecast(model2, h=500))
```
**Explanation:**

1.  **Auto ARIMA:** gave order of ARIMA (4,0,4)

    i.e. no autoregressive (AR) terms, no differencing (D) terms, and one moving average (MA) term.

2.  **Log likelihood:** 4476.69 This is a measure of the model's goodness of fit. A higher log likelihood indicates a better fit.

    **AIC:** -8935.38 The Akaike Information Criterion (AIC) is a measure of model complexity and fit. A lower AIC indicates a better model.

    **sigma\^2:** 0.0001553 This is the estimated variance of the residuals, representing the model's ability to fit the data. A smaller value suggests a better fit.

    **Implication:** The ARIMA(4,0,4) model provides a parsimonious representation of the LRNSEI time series. The model suggests that the current value of the series is influenced by the previous period's error.

3.  **The significance test** indicate that the MA1 coefficient in the ARIMA(4,0,4) model is not statistically significant. The intercept coefficient is close to being statistically significant, but more evidence is needed to confirm its significance.

**3.N225**

```{r}
acf(LRN225) 
pacf(LRN225) 

#Using Auto arima 
arma_pq_LRN225 = auto.arima(LRN225); arma_pq_LRN225

#Application of ARIMA

model2 = arima(LRN225,order = c(0,0,0))
model2

et = residuals(model2)
et

#Checking of significance of ARMA
coeftest(model2)

#point forecast is called out of sample forecast
autoplot(forecast(model2, h=500))
```
**Explanation:**

1.  **Auto ARIMA:** gave order of ARIMA (0,0,0)

    i.e. no autoregressive (AR) terms, no differencing (D) terms, and one moving average (MA) term.

2.  **Log likelihood:** 4371.79 This is a measure of the model's goodness of fit. A higher log likelihood indicates a better fit.

    **AIC:** -8741.58 The Akaike Information Criterion (AIC) is a measure of model complexity and fit. A lower AIC indicates a better model.

    **sigma\^2:** 0.0001486 This is the estimated variance of the residuals, representing the model's ability to fit the data. A smaller value suggests a better fit.

    **Implication:** The ARIMA(0,0,0) model provides a parsimonious representation of the LRNSEI time series. The model suggests that the current value of the series is influenced by the previous period's error.

3.  **The significance test** indicate that the MA1 coefficient in the ARIMA(0,0,0) model is not statistically significant. The intercept coefficient is close to being statistically significant, but more evidence is needed to confirm its significance.
**4.HSI**

```{r}
acf(LRHSI) 
pacf(LRHSI) 

#Using Auto arima 
arma_pq_LRHSI = auto.arima(LRHSI); arma_pq_LRHSI

#Application of ARIMA

model2 = arima(LRHSI,order = c(0,0,0))
model2

et = residuals(model2)
et

#Checking of significance of ARMA
coeftest(model2)

#point forecast is called out of sample forecast
autoplot(forecast(model2, h=500))
```
**Explanation:**

1.  **Auto ARIMA:** gave order of ARIMA (0,0,0)

    i.e. no autoregressive (AR) terms, no differencing (D) terms, and no moving average (MA) terms.

2.  **sigma\^2**: 0.0002079. This is the estimated variance of the residuals, representing the model's ability to fit the data.

    **Log likelihood:** 4160.01. A higher log likelihood indicates a better fit.

    **AIC:** -8316.03. A lower AIC indicates a better model.

    **Implication:** The ARIMA(0,0,0) model suggests that the LRHSI time series is a white noise process. This indicates that there are no predictable patterns or trends in the data.

3.  **The significance test** The significance test suggests that the intercept coefficient in the ARIMA(0,0,0) model is not statistically significant.
**5.N100**

```{r}
acf(LRN100) 
pacf(LRN100) 

#Using Auto arima 
arma_pq_LRN100 = auto.arima(LRN100); arma_pq_LRN100

#Application of ARIMA

model2 = arima(LRHSI,order = c(0,0,0))
model2

et = residuals(model2)
et

#Checking of significance of ARMA
coeftest(model2)

#point forecast is called out of sample forecast
autoplot(forecast(model2, h=500))
```
**Explanation:**

1.  **Auto ARIMA:** gave order of ARIMA (0,0,0)

    no autoregressive (AR) terms, no differencing (D) terms, and no moving average (MA) terms.

2.  **sigma\^2:** 0.0001351. This is the estimated variance of the residuals, representing the model's ability to fit the data.

    **Log likelihood:** 4662.94. A higher log likelihood indicates a better fit.

    **AIC:** -9321.89. A lower AIC indicates a better model.

    **Implication:** The ARIMA(0,0,0) model suggests that the LRN100 time series is a white noise process. This indicates that there are no predictable patterns or trends in the data.

3.  **The significance test** The significance test suggests that the intercept coefficient in the ARIMA(0,0,0) model is not statistically significant. This supports the conclusion that the LRN100 series is a white noise process with a mean close to zero.



**Linearity Test:**

**Used Test:** BDS Test

**H0:** There is linearity in log returns of series

**H1:** There is no linearity in log returns of series
```{r}
bds_result_BSESN <- bds.test(LRBSESN)

# Print the result
print(bds_result_BSESN)
#BSESN data is non linear
```

```{r}
bds_result_GSPC <- bds.test(LRGSPC)

# Print the result
print(bds_result_GSPC)
#GSPC data is non linear
```

```{r}
bds_result_N225 <- bds.test(LRN225)

# Print the result
print(bds_result_N225)
#N225 data is non linear
```

```{r}
bds_result_HSI <- bds.test(LRHSI)

# Print the result
print(bds_result_HSI)
#HSI data is non linear
```

```{r}
bds_result_N100 <- bds.test(LRN100)

# Print the result
print(bds_result_N100)
#N100 data is non linear
```
**Explanation:**

p-value for all 5 series is less than 0.05

hence we reject the null hypothesis and say that there is no linearity in log returns of any series

Implication: Since series is not linear, a SETAR model might be a more appropriate choice for modeling the log return series. The SETAR model can capture the non-linear relationships and threshold effects present in the data.



**BSESN:**
```{r}
VARselect(LRBSESN)
#AIC lag is 10
selectSETAR(LRBSESN, m=2, thDelay = 1)
mod.setar1 = setar(LRBSESN, m=2, thDelay = 1, th= -0.007846886)
summary(mod.setar1)
```
**Explanation:**

**AIC order:** 10\
**Hence Threshold value:** -0.007846886

**Implication:** The SETAR model provides a suitable framework for capturing the non-linear dynamics in the time series data. The results indicate significant differences in the dynamics between the high and low regimes, suggesting that the threshold is an important factor in understanding the series' behavior.

**GSPC:**
```{r}
VARselect(LRGSPC)
#AIC lag is 9
selectSETAR(LRGSPC, m=2, thDelay = 1)
mod.setar2 = setar(LRGSPC, m=2, thDelay = 1, th= -0.007264115)
summary(mod.setar2)
```
**Explanation:**

**AIC order:** 9\
**Hence Threshold value:** -0.007264115

**Implication:** The SETAR model provides a suitable framework for capturing the non-linear dynamics in the time series data. The results indicate significant differences in the dynamics between the high and low regimes, suggesting that the threshold is an important factor in understanding the series' behavior.

**N225:**
```{r}
VARselect(LRN225)
#AIC lag is 7
selectSETAR(LRN225, m=2, thDelay = 1)
mod.setar3 = setar(LRN225, m=2, thDelay = 1, th= -0.008663830)
summary(mod.setar3)
```
**Explanation:**

**AIC order:** 7\
**Hence Threshold value:** -0.008663830

**Implication:** The SETAR model provides a suitable framework for capturing the non-linear dynamics in the time series data. The results indicate significant differences in the dynamics between the high and low regimes, suggesting that the threshold is an important factor in understanding the series' behavior.


**HSI:**
```{r}
VARselect(LRHSI)
#AIC lag is 6
selectSETAR(LRHSI, m=2, thDelay = 1)
mod.setar4 = setar(LRHSI, m=2, thDelay = 1, th= -0.01201875)
summary(mod.setar4)
```
**Explanation:**

**AIC order:** 10\
**Hence Threshold value:** -0.01201875

**Implication:** The SETAR model provides a suitable framework for capturing the non-linear dynamics in the time series data. The results indicate significant differences in the dynamics between the high and low regimes, suggesting that the threshold is an important factor in understanding the series' behavior.

**N100:**
```{r}
VARselect(LRN100)
#AIC lag is 8
selectSETAR(LRN100, m=2, thDelay = 1)
mod.setar5 = setar(LRN100, m=2, thDelay = 1, th= -0.006764070)
summary(mod.setar5)
```
**Explanation:**

**AIC order:** 10\
**Hence Threshold value:** -0.006764070

**Implication:** The SETAR model provides a suitable framework for capturing the non-linear dynamics in the time series data. The results indicate significant differences in the dynamics between the high and low regimes, suggesting that the threshold is an important factor in understanding the series' behavior.




**Random Walk and Market Efficiency Check for all 5 returns series:**

**Test 1: Automatic Variance Ratio Test**

H0: follows random walk and has weak form of mkt efficiency i.e. mkt is not predictable

if critical value \> 1.96, we reject the null hypothesis

**Test 2: Automatic Portmanteau Test**

H0: follows random walk and has weak form of mkt efficiency i.e. mkt is not predictable

if critical value \> 1.96, we reject the null hypothesis

**Test 3: Hurst Exponent Test**

H= 0.5 or near : follows random walk

H= 0 or near: short memory

H= 1 or near: long memory


**BSESN:**
```{r}
# RANDOM WALK MODEL
Auto.VR(LRBSESN)
Auto.Q(LRBSESN)
hurstexp(LRBSESN)
```
**Explanation:**

Automatic Variance Ratio test suggests series does not follow random walk model

Automatic Portmanteau Test suggests series follows random walk model

Hurst Exponent suggests series follows random walk model

Automatic Variance Ratio test is more reliable hence we say the NSEI returns series **does not follow random walk and stock has some degree of market inefficiency**


**GSPC:**
```{r}
Auto.VR(LRGSPC)
Auto.Q(LRGSPC)
hurstexp(LRGSPC)
```

**Explanation:**

Automatic Variance Ratio test suggests series does not follow random walk model

Automatic Portmanteau Test suggests series does not follow random walk model

Hurst Exponent suggests series follows random walk model

Automatic Variance Ratio test is more reliable hence we say the GSPC returns series **does not follow random walk and stock has some degree of market inefficiency**

**N225:**
```{r}
Auto.VR(LRN225)
Auto.Q(LRN225)
hurstexp(LRN225)
```

**Explanation:**

Automatic Variance Ratio test suggests series does not follow random walk model

Automatic Portmanteau Test suggests series does not follow random walk model

Hurst Exponent suggests series follows random walk model

Automatic Variance Ratio test is more reliable hence we say the GSPC returns series **does not follow random walk and stock has some degree of market inefficiency**

**HSI:**
```{r}
Auto.VR(LRHSI)
Auto.Q(LRHSI)
hurstexp(LRHSI)
```

**Explanation:**

Automatic Variance Ratio test suggests series follows random walk model

Automatic Portmanteau Test suggests series follows random walk model

Hurst Exponent suggests series follows random walk model

From all three tests we can say the HSI returns series **follows random walk and stock has weak form of market efficiency**

**N100:**
```{r}
Auto.VR(LRN100)
Auto.Q(LRN100)
hurstexp(LRN100)
```
**Explanation:**

Automatic Variance Ratio test suggests series follows random walk model

Automatic Portmanteau Test suggests series follows random walk model

Hurst Exponent suggests series follows random walk model

From all the 3 tests we say the N100 returns series **follows random walk and stock has weak form of market efficiency**



**ARCH & GARCH Test for all 5 series:**

To include stylised facts of returns series into forecasting, we will move ahead to forecasting with ARCH & GARCH for all of our returns series

**ARCH Test:**

AutoRegressive Conditional Heteroskedasticity Test

H0: There is no ARCH effect in the returns series of data

H1: There is ARCH effect in the returns series of data


**BSESN:**
```{r}
#step 2: ARCH effect test
ArchTest(LRBSESN)  #p-value < 0.05, there is ARCH effect
#there is ARCH effect

# step3: ARCH/GARCH order
garch(LRBSESN, grad="numerical",trace=FALSE)

#step 4: Application of ARCH and GARCH
x=ugarchspec(variance.model = list(garchOrder=c(1,1)),mean.model = list(armaOrder=c(0,0)))
x_fit=ugarchfit(x,data=LRBSESN)
x_fit
```
## News Impact Curve
```{r}
x=newsimpact(x_fit)
plot(x$zx, x$zy, type="l", lwd=2, col="blue", main="GARCH(1,1) - News Impact", ylab=x$yexpr, xlab=x$xexpr)
```
## e-GARCH (For asymmetry)
```{r}
model1=ugarchspec(variance.model = list(model="eGARCH",garchOrder=c(1,1)),mean.model = list(armaOrder=c(0,0)))
fitmodel1=ugarchfit(model1,data=LRBSESN)
fitmodel1
```

**Explanation:**

e-GARCH test is done when there is asymmetry in volatility of returns and when there is leverage effect

here is **gamma value \> 0** i.e. positive hence there is no leverage effect in the data

hence we cannot forecast with e-GARCH model and hence we will forecast the volatility with GARCH model.

```{r}
ugarchforecast(x_fit, n.ahead=20)
```


**GSPC:**
```{r}
#step 2: ARCH effect test
ArchTest(LRGSPC)  #p-value < 0.05, there is ARCH effect
#there is ARCH effect
# step3: ARCH/GARCH order
garch(LRGSPC, grad="numerical",trace=FALSE)

#step 4: Application of ARCH and GARCH
x=ugarchspec(variance.model = list(garchOrder=c(1,1)),mean.model = list(armaOrder=c(0,0)))
x_fit1=ugarchfit(x,data=LRGSPC)
x_fit1
```

**Explanation:**

ARCH test suggests that there is ARCH effect in the data hence we can move ahead to do GARCH forecasting of the series

GARCH gave ARCH,GARCH order of 1,1

Sign Bias Test suggest that there is no significant effect of positive and negative bias individually.

but there is collective effect of both the signs on returns of series. hence there is **asymmetry in volatility of returns**

## News Impact Curve
```{r}
x=newsimpact(x_fit1)
plot(x$zx, x$zy, type="l", lwd=2, col="blue", main="GARCH(1,1) - News Impact", ylab=x$yexpr, xlab=x$xexpr)
```

## e-GARCH (For asymmetry)
```{r}
model2=ugarchspec(variance.model = list(model="eGARCH",garchOrder=c(1,1)),mean.model = list(armaOrder=c(0,0)))
fitmodel2=ugarchfit(model2,data=LRGSPC)
fitmodel2
```

**Explanation:**

e-GARCH test is done when there is asymmetry in volatility of returns and when there is leverage effect

here is **gamma value \> 0** i.e. positive hence there is no leverage effect in the data

hence we cannot forecast with e-GARCH model and hence we will forecast the volatility with GARCH model.
```{r}
ugarchforecast(x_fit1, n.ahead=20)
```

**N225:**
```{r}
#step 2: ARCH effect test
ArchTest(LRN225)  #p-value < 0.05, there is ARCH effect
#there is ARCH effect

# step3: ARCH/GARCH order
garch(LRN225, grad="numerical",trace=FALSE)
#step 4: Application of ARCH and GARCH
x=ugarchspec(variance.model = list(garchOrder=c(1,1)),mean.model = list(armaOrder=c(0,0)))
x_fit2=ugarchfit(x,data=LRN225)
x_fit2
```
**Explanation:**

ARCH test suggests that there is ARCH effect in the data hence we can move ahead to do GARCH forecasting of the series

GARCH gave ARCH,GARCH order of 1,1

Sign Bias Test suggest that there is no significant effect of positive and negative bias individually.

but there is collective effect of both the signs on returns of series. hence there is **asymmetry in volatility of returns**

## News Impact Curve
```{r}
x=newsimpact(x_fit2)
plot(x$zx, x$zy, type="l", lwd=2, col="blue", main="GARCH(1,1) - News Impact", ylab=x$yexpr, xlab=x$xexpr)
```
## e-GARCH (For asymmetry)
```{r}
model3=ugarchspec(variance.model = list(model="eGARCH",garchOrder=c(1,1)),mean.model = list(armaOrder=c(0,0)))
fitmodel3=ugarchfit(model3,data=LRN225)
fitmodel3
```
**Explanation:**

e-GARCH test is done when there is asymmetry in volatility of returns and when there is leverage effect

here is **gamma value \> 0** i.e. positive hence there is no leverage effect in the data

hence we cannot forecast with e-GARCH model and hence we will forecast the volatility with GARCH model.
```{r}
ugarchforecast(x_fit2, n.ahead=20)
```

**HSI:**
```{r}
#step 2: ARCH effect test
ArchTest(LRHSI)  #p-value < 0.05, there is ARCH effect
#there is ARCH effect

# step3: ARCH/GARCH order
garch(LRHSI, grad="numerical",trace=FALSE)

#step 4: Application of ARCH and GARCH
x=ugarchspec(variance.model = list(garchOrder=c(1,1)),mean.model = list(armaOrder=c(0,0)))
x_fit3=ugarchfit(x,data=LRHSI)
x_fit3
```
**Explanation:**

ARCH test suggests that there is ARCH effect in the data hence we can move ahead to do GARCH forecasting of the series

GARCH gave ARCH,GARCH order of 1,1

The lack of significant overall sign bias and individual sign biases suggests that the **impact of positive and negative shocks on the variance is symmetric**. This means that positive and negative shocks have similar effects on the volatility of the time series.

## News Impact Curve
```{r}
x=newsimpact(x_fit3)
plot(x$zx, x$zy, type="l", lwd=2, col="blue", main="GARCH(1,1) - News Impact", ylab=x$yexpr, xlab=x$xexpr)
```
## e-GARCH (For asymmetricity)
```{r}
model4=ugarchspec(variance.model = list(model="eGARCH",garchOrder=c(1,1)),mean.model = list(armaOrder=c(0,0)))
fitmodel4=ugarchfit(model3,data=LRHSI)
fitmodel4
```
**Explanation:**

e-GARCH test is done when there is asymmetry in volatility of returns and when there is leverage effect

here is **gamma value \> 0** i.e. positive hence there is no leverage effect in the data

hence we cannot forecast with e-GARCH model and hence we will forecast the volatility with GARCH model.
```{r}
ugarchforecast(x_fit3, n.ahead=20)
```

**HSI:**
```{r}
#step 2: ARCH effect test
ArchTest(LRN100)  #p-value < 0.05, there is ARCH effect
#there is ARCH effect

# step3: ARCH/GARCH order
garch(LRN100, grad="numerical",trace=FALSE)

#step 4: Application of ARCH and GARCH
x=ugarchspec(variance.model = list(garchOrder=c(1,1)),mean.model = list(armaOrder=c(0,0)))
x_fit4=ugarchfit(x,data=LRN100)
x_fit4
```
## News Impact Curve

```{r}
x=newsimpact(x_fit4)
plot(x$zx, x$zy, type="l", lwd=2, col="blue", main="GARCH(1,1) - News Impact", ylab=x$yexpr, xlab=x$xexpr)
```
## e-GARCH (For asymmetricity)
```{r}
model5=ugarchspec(variance.model = list(model="eGARCH",garchOrder=c(1,1)),mean.model = list(armaOrder=c(0,0)))
fitmodel5=ugarchfit(model5,data=LRN100)
fitmodel5
```

**Explanation:**

e-GARCH test is done when there is asymmetry in volatility of returns and when there is leverage effect

here is **gamma value \> 0** i.e. positive hence there is no leverage effect in the data

hence we cannot forecast with e-GARCH model and hence we will forecast the volatility with GARCH model.
```{r}
ugarchforecast(x_fit4, n.ahead=20)
```
